### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
updating reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: don't we explain that on Functionalities section? Any ideia what else we could add? The problem is that we have page limit, right? Can you please mail the editor and check if we can exceed the page limit to properly handle the reviewer comments?}}
\end{quote}

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} We have improved Functionalities section, in order to include more details about ESBMC-GPU's capabilities.}
\end{quote}
